A Flux Scale for Southern Hemisphere 21cm EoR Experiments

### 2013-05-13 ms.tex
updating to latest cal

%\title{The Reionization flux scale in the Southern Sky}
\title{A Flux Scale for Southern Hemisphere 21cm EoR Experiments}
\author{
Daniel C. Jacobs\altaffilmark{1},
Aaron R. Parsons\altaffilmark{2},
James E. Aguirre\altaffilmark{3},
Zaki Ali\altaffilmark{2},
Richard F. Bradley\altaffilmark{4,5,6},
Chris L.  Carilli\altaffilmark{7},
David R. DeBoer\altaffilmark{8},
Matthew R. Dexter\altaffilmark{8},
Nicole E. Gugliucci\altaffilmark{5},
Pat Klima\altaffilmark{5},
Dave H. E. MacMahon\altaffilmark{8},
Jason R. Manley\altaffilmark{9},
David F. Moore\altaffilmark{3},
Jonathan C. Pober\altaffilmark{2},
Irina I. Stefan\altaffilmark{10},
William P. Walbrugh\altaffilmark{9}}

@@

% XXX elaborate on:
%However, catalog source fluxes at 150MHz are also inaccurate to the 20\% level,
%particularly at southern declinations ($\delta<-20$\arcdeg). 
% not sure where this went. -dcj

% XXX remove PAPER specificity from below?
EoR measurements in the southern sky have focused on the coldest regions where
galactic foregrounds are minimal. With the majority of possible observing time falling on 
RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
(5h19m49.1 -45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
 similar to Cygnus A.  At $\sim$400Jy Pictor is bright and sufficiently distant from other 
bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
size of $\sim$8\arcmin is smaller than the scales being probed by current EoR instruments , 
making resolution effects, making it suitable for precision calibration.  However, 
like most other sources, precise flux measurements in the EoR band are not available.
The current best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.

% XXX more background on pictor A
%  added dcj
%0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
% XXX transition to the PAPER instrument
Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012a}.
Though highly sensitive as a power spectrum instrument, the maximally redundant
has a broad point spread function and is able to measure only the brightest sources,
like Pictor A, for flux calibration purposes.  
% XXX to calibrate these observations...
% added dcj

\section{Approach}
\label{sec:approach}
% XXX incorporate
Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
on -45\arcdeg.

@@

As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. Each source track
provides a detailed measurement of the primary beam relative to the peak of the measured flux. However,
a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
some rate depending on the accuracy of the slope of the beam model, limiting our declination range ($\Delta \delta$).

EQUATION FOR BEAM ERROR %XXX
% \[
% g(\alpha,\delta) = \frac{d B(\theta,\phi)}{d\delta} \Delta \delta 
% \]
Using our source tracks, we can measure the slope of the beam and compare with models over a range of angles

EQUATION FOR BEAM ERROR ALONG SOURCE TRACK %XXX

As we see in Figure XXX the model beam is able to predict the measured beam slope across a 5\arcdeg
distance to within XXX\%.

\[
B_M = B_M(\theta(t),\phi(t))\\
\sim 0.02\\
\Delta B /B_M= \Delta (S_p)/B^2_M \sim \Delta B_M \\
(\Delta B - \Delta B_M)/B_M < 0.01
\]

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/2250-412_2331-416_2140-434_0007-446_0704-427_gain_mcmc_chain_gain_conf.png}
\caption{
The marginalized PAPER flux scale factor posterior probability distribution
function bootstrapped from the NED database listings for
2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
\label{fig:gain}}
\end{figure*}

@@

%BEGIN PASTE

@@

\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.1064
\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %0.1851
\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %0.7325
\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.2527
\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.0596
\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %0.2988
\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.007
\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %2.3481
\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0595
\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %2.6709
\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %2.6256
\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1024

@@

\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1044
\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8893
\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.709
\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0824
\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.3377
\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0699
\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %1.2296
\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %1.5069
\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0031
\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0455
\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0055
\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.0592

@@

\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.4795
\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %0.891
\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0056
\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %0.973
\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.0961
\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %0.9684
\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %1.4713
\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0157
\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %2.7782
\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %0.2602
\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.135
\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1159

@@

\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.0164
\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0524
\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.0739
\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.3123
\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.1767
\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.1166
\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.2199
\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %6.9237
\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.2179

@@

\caption{fits of the next 16 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a

@@

%BEGIN PASTE
%ok fit, but doesn't agree with past data, or actually increases model uncertainty
%contour length limit =  209.039667221
%Poor improvement:  1116-462 8.66,9.97,11.27 -0.72,-0.59,-0.47 8.56,9.82,11.15 -0.71,-0.58,-0.46 0.22 0.23 -0 0.6 -0.0018 164.0
\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %-0.0018
%Poor improvement:  1143-483 13.47,15.46,17.58 -0.83,-0.7,-0.57 9.91,11.65,13.51 -0.7,-0.56,-0.44 0.34 0.37 -0.03 0.21 -0.0064 122.0
\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %-0.0064
%Poor improvement:  1215-457 15.08,16.94,18.88 -0.59,-0.47,-0.36 11.28,12.93,14.57 -0.46,-0.33,-0.21 0.36 0.39 -0.03 0.15 -0.0042 122.0
\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %-0.0042
%Poor improvement:  1221-423 9.46,11.52,13.87 -0.96,-0.78,-0.61 6.77,8.6,10.49 -0.78,-0.57,-0.39 0.45 0.53 -0.08 0.27 -0.022 116.0
\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %-0.022
%Poor improvement:  1232-416 9.42,10.83,12.3 -0.88,-0.75,-0.63 9.2,10.57,11.96 -0.88,-0.74,-0.62 0.22 0.22 -0 0.57 -0.002 164.0
\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %-0.002
%Poor improvement:  1407-425 13.6,15.19,16.86 -1.21,-1.09,-0.98 9.91,11.35,12.85 -1.07,-0.94,-0.82 0.36 0.41 -0.05 0.11 -0.0059 128.0
\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0059

@@

\caption{fits of the worst sources. Contours as described in Figure \ref{fig:SI_contour_1}. The fit either disagrees
with past data or does not offer any improvement (improvement index $\le 0$). All are near
the galactic plane and are likely dominated by sidelobes.
}\label{fig:SI_contour_bad}

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %-0
\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
\end{center}
\caption{
These sources offer results at odds with previous measurements. These have
small enough error bars to require a deviation from spectral index fit
suggested by prior catalog measurements. All are near Centaurus A (see Figure
\ref{fig:error_map}), a very bright, extended source, and are likely evidence
for side lobe contamination.  Side lobes from distant sources manifest as
ripples in the spectrum, increasing the error bars (e.g. the sources listed in
Figure \ref{fig:SI_contour_bad}). However, the sources shown here are close
enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
and does not fall into the rms, but rather into the mean. Thus these few points
have anomalously high fluxes and small error bars. 
} \label{fig:SI_contour_new}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.png}
\caption{
A map of the radio sky centered on the south pole
\citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
scaled by agreement with prior data (inverse ``improvement index", see
\S\ref{sec:fits}). Black dots indicate sources with $\le0$ improvement score.
For these the fit quality decreases with addition of PAPER data or the model
revision disagrees completely with the prior estimate due to side lobes or
spectral curvature.  We estimate that   \label{fig:error_map}
}
\end{figure*}

>>>>

%\title{The Reionization flux scale in the Southern Sky}
\title{A Flux Scale for Southern Hemisphere 21cm EoR Experiments}
\author{
Daniel C. Jacobs\altaffilmark{1},
Aaron R. Parsons\altaffilmark{2},
James E. Aguirre\altaffilmark{3},
Zaki Ali\altaffilmark{2},
Richard F. Bradley\altaffilmark{4,5,6},
Chris L.  Carilli\altaffilmark{7},
David R. DeBoer\altaffilmark{8},
Matthew R. Dexter\altaffilmark{8},
Nicole E. Gugliucci\altaffilmark{5},
Pat Klima\altaffilmark{5},
Dave H. E. MacMahon\altaffilmark{8}
Jason R. Manley\altaffilmark{9},
David F. Moore\altaffilmark{3},
Jonathan C. Pober\altaffilmark{2},
Irina I. Stefan\altaffilmark{10},
William P. Walbrugh\altaffilmark{9}}

@@

EoR measurements in the southern sky have focused on the coldest regions where
galactic foregrounds are minimal. With the majority of possible observing time falling on 
RA=4h,Dec=-30. The brightest and least-resolved calibrator in this region is Pictor A 
(5h19m49.1 -45d46m45.0). Pictor A is a nearby FR-II type radio galaxy 
 similar to Cygnus A.  At $\sim$400Jy Pictor is bright and sufficiently distant from other 
bright sources to make it eminently suitable as both a phase and flux calibrator. Its apparent
size of $\sim$8\arcmin is smaller than the scales being probed by current EoR instruments , 
making resolution effects, making it suitable for precision calibration.  However, 
like most other sources, precise flux measurements in the EoR band are not available.
The current best EoR band measurement
is uncertain to 12\% and appears to imply spectral flattening in the EoR band
\citep{Perley:1997p9312}.

%0518-458	 PKS, Pictor A	G	 25.93	 24.01	1		W	 0.0342	 23.63	 176.
% XXX transition to the PAPER instrument
Establishing an accurate spectrum for Pictor A is of particular importance for
PAPER --- a dedicated EoR experiment 
that employs drift-scanning, dual-polarization dipole antennas 
tuned for efficient operation over a 120--170-MHz band.  PAPER is located in the South African Karoo desert
on the Square Kilometer Array
South Africa (SKA-SA) reserve, 100km north of the small town of Carnarvon.
The PAPER array has grown from 16 elements deployed in early 2009 to a
64-element imaging array in 2011 (see Figure \ref{fig:antpos}). 
Since November 2011 it has been arranged in a maximally redundant grid 
configuration to make deep power spectral integrations \citep{Parsons:2012a}.
Though highly sensitive as a power spectrum instrument, the maximally redundant array 
has a broad point spread function in the image domain. This severely limits the number 
of sources which may be used for flux calibration. Drift scanning across the sky with a 45\arcdeg FWHM
primary beam there are very few unresolved, bright sources which are far from the galactic plane. 
Pictor A is bright and well enough separated from other emission to dominate the visibilities for a good fraction of
the EoR observing season, making it an ideal flux calibrator.

\section{Approach}
\label{sec:approach}
Given the large uncertainties in the literature, and the necessity for PAPER power-spectrum analysis
to use Pictor A for flux calibration, we felt it prudent to examine Pictor A directly.
In this section, we describe how we use PAPER in its imaging configuration
to measure Pictor A and a selection of known, bright sources in a 5\arcdeg strip centered
on -45\arcdeg.

@@

As PAPER is a drift scan instrument, each declination $\delta$ describes a distinct cut through the primary beam. These cuts
provide a detailed measurement of the primary beam relative to the peak of the trace, however,
a model $g(\delta)$ is still required to calibrate between declinations. This model will be effective over a range of declinations, but will diverge at
some rate depending on the accuracy with which the model describes the slope.  As an estimate of the extrapolated 
beam amplitude we fit the slope of our Pictor A source track and compute the amplitude extrapolated over our fiducial
stripe width of 5\arcdeg.

\[
B = dB/dt dt/\theta \Delta \theta
\]

Comparing this with the simulation in Figure \ref{fig:beam_extrapolation}, we find that the model predicts the 5\arcdeg extrapolation to better
than 2\% even into the more uncertain areas far from zenith. The RMS difference for the central 15\arcdeg of the track
is 1.5\%. From this we conclude that, as long as we constrain our extrapolations to $\pm5$\arcdeg around Pictor A,
we will have negligible beam area.

\begin{figure*}
\includegraphics[width=.9\textwidth]{plots/beam_slope_compare.png}
\caption{The beam is well along a declination cut but beam formed source tracks. Here we measure the beam, 
as extrapolated by fitting a slope (dotted), and compare with the beam model (solid). The difference (circles) is never larger
than $\sim$1\%.  Thus we conclude that the beam slope is locally well modeled and our beam model is suitable 
for extrapolation over $\sim$5\arcdeg scales.
  \label{fig:beam_extrapolation}}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=0.9\textwidth]{plots/1526-423_2250-412_2331-416_1932-464_1421-490_gain_mcmc_chain_gain_conf.png}
\caption{
The marginalized PAPER flux scale factor posterior probability distribution
function bootstrapped from the NED database listings for
2250-412,2331-416,2140-434,0007-446 and 0704-427 below 2GHz.
\label{fig:gain}}
\end{figure*}

@@

%TOP OF MAIN CONFIDENCE PLOT SECTION

@@

\includegraphics[width=2in]{plots/0003-428_SI_MCMC.png} %0.9878
\includegraphics[width=2in]{plots/0007-446_SI_MCMC.png} %1.0085
\includegraphics[width=2in]{plots/0039-445_SI_MCMC.png} %1.3403
\includegraphics[width=2in]{plots/0043-424_SI_MCMC.png} %0.5959
\includegraphics[width=2in]{plots/0048-447_SI_MCMC.png} %0.6165
\includegraphics[width=2in]{plots/0049-433_SI_MCMC.png} %1.0632
\includegraphics[width=2in]{plots/0103-453_SI_MCMC.png} %0.1456
\includegraphics[width=2in]{plots/0201-440_SI_MCMC.png} %3.0727
\includegraphics[width=2in]{plots/0438-436_SI_MCMC.png} %0.0991
\includegraphics[width=2in]{plots/0511-484_SI_MCMC.png} %3.3967
\includegraphics[width=2in]{plots/0534-497_SI_MCMC.png} %3.4118
\includegraphics[width=2in]{plots/0546-445_SI_MCMC.png} %0.1647

@@

\includegraphics[width=2in]{plots/0547-408_SI_MCMC.png} %0.1506
\includegraphics[width=2in]{plots/0647-475_SI_MCMC.png} %0.8384
\includegraphics[width=2in]{plots/0700-473_SI_MCMC.png} %1.9848
\includegraphics[width=2in]{plots/0704-427_SI_MCMC.png} %0.0785
\includegraphics[width=2in]{plots/0748-440_SI_MCMC.png} %0.2942
\includegraphics[width=2in]{plots/0748-454_SI_MCMC.png} %0.0742
\includegraphics[width=2in]{plots/0809-492_SI_MCMC.png} %0.6265
\includegraphics[width=2in]{plots/0819-474_SI_MCMC.png} %0.9749
\includegraphics[width=2in]{plots/1017-421_SI_MCMC.png} %0.0034
\includegraphics[width=2in]{plots/1017-426_SI_MCMC.png} %0.0195
\includegraphics[width=2in]{plots/1046-409_SI_MCMC.png} %0.0012
\includegraphics[width=2in]{plots/1116-462_SI_MCMC.png} %0.0062

@@

\includegraphics[width=2in]{plots/1143-483_SI_MCMC.png} %0.004
\includegraphics[width=2in]{plots/1215-457_SI_MCMC.png} %0.0163
\includegraphics[width=2in]{plots/1232-416_SI_MCMC.png} %0.0227
\includegraphics[width=2in]{plots/1243-412_SI_MCMC.png} %0.0076
\includegraphics[width=2in]{plots/1246-410_SI_MCMC.png} %0.06
\includegraphics[width=2in]{plots/1247-401_SI_MCMC.png} %0.1161
\includegraphics[width=2in]{plots/1302-491_SI_MCMC.png} %0.5328
\includegraphics[width=2in]{plots/1355-416_SI_MCMC.png} %0.1959
\includegraphics[width=2in]{plots/1358-493_SI_MCMC.png} %0.7284
\includegraphics[width=2in]{plots/1421-490_SI_MCMC.png} %1.3529
\includegraphics[width=2in]{plots/1424-418_SI_MCMC.png} %0.0218
\includegraphics[width=2in]{plots/1445-468_SI_MCMC.png} %1.8104

@@

\includegraphics[width=2in]{plots/1526-423_SI_MCMC.png} %0.1985
\includegraphics[width=2in]{plots/1552-433_SI_MCMC.png} %1.3211
\includegraphics[width=2in]{plots/1556-466_SI_MCMC.png} %2.5579
\includegraphics[width=2in]{plots/1616-457_SI_MCMC.png} %0.0507
\includegraphics[width=2in]{plots/1618-430_SI_MCMC.png} %3.821
\includegraphics[width=2in]{plots/1633-409_SI_MCMC.png} %1.3843
\includegraphics[width=2in]{plots/1839-487_SI_MCMC.png} %0.1766
\includegraphics[width=2in]{plots/1840-404_SI_MCMC.png} %0.1658
\includegraphics[width=2in]{plots/1932-464_SI_MCMC.png} %0.4321
\includegraphics[width=2in]{plots/1940-406_SI_MCMC.png} %0.0325
\includegraphics[width=2in]{plots/1953-425_SI_MCMC.png} %0.1181
\includegraphics[width=2in]{plots/2140-434_SI_MCMC.png} %0.2976

@@

@@

\includegraphics[width=2in]{plots/2213-456_SI_MCMC.png} %0.2146
\includegraphics[width=2in]{plots/2226-411_SI_MCMC.png} %0.3157
\includegraphics[width=2in]{plots/2250-412_SI_MCMC.png} %0.5585
\includegraphics[width=2in]{plots/2323-407_SI_MCMC.png} %4.9008
\includegraphics[width=2in]{plots/2331-416_SI_MCMC.png} %0.8134

@@

\caption{fits of the last 5 sources, as described in Figure \ref{fig:SI_contour_1}. Sources marked with a
}\label{fig:SI_contour_5}
\end{figure*}%BOTTOM OF MAIN CONFIDENCE PLOT SECTION
%%%%%%%%%%%%%%%%%%%%

%BEGIN PASTE
\begin{figure*}[htbp]
\begin{center}
%ok fit, but doesn't agree with past data, or actually increases model uncertainty
%contour length limit =  223.105907705
%Poor improvement:  1407-425 14.03,15.48,16.92 -1.23,-1.11,-0.99 9.88,11.36,12.93 -1.08,-0.95,-0.82 0.4 0.41 -0.01 0.07 -0.0006 118.0
\includegraphics[width=2in]{plots/1407-425_SI_MCMC.png} %-0.0006
\caption{Contours of spectral fit as described in Figure \ref{fig:SI_contour_1}. This source displays negative 
improvement. The addition of the PAPER data actually slightly increases the uncertainty.
\label{fig:SI_contour_bad}}
\end{center}
\end{figure*}

\begin{figure*}[htbp]
\begin{center}
%zero overlap
\includegraphics[width=2in]{plots/1221-423_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1315-460_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1320-446_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1416-493_SI_MCMC.png} %0.0
\includegraphics[width=2in]{plots/1459-417_SI_MCMC.png} %0
\includegraphics[width=2in]{plots/cen_SI_MCMC.png} %0.0
\end{center}
\caption{
These sources are at odds with previous measurements.
Two simply do not have enough
prior catalog data to fit a spectral model, while the rest have
suggest a deviation from the catalog spectral index fit.
All are near Centaurus A (see Figure
\ref{fig:error_map}), a very bright, extended source, as well as the galactic plane.
Side lobes manifest as
ripples in the beam formed spectra which increases the error bars. See for example the 
Pictor A spectrum \ref{fig:pic_spectrum_detail}. However, the sources shown here are close
enough to Centaurus A that the side-lobe oscillates on scales longer than 10MHz
and does not fall into the rms, but rather into the mean. Thus these few points
have anomalously high fluxes and small error bars. 
} \label{fig:SI_contour_new}
\end{figure*}

@@

\begin{figure*}
\includegraphics[width=\textwidth]{plots/psa64_pic_strip_positions_annotated_cropped.pdf}
\caption{
A map of the radio sky centered on the south pole
\citep{deOliveiraCosta:2008p2242}.  x's mark measured locations and have size
scaled by dis-agreement with prior data (inverse ``improvement index" from 
\S\ref{sec:fits}). Smaller indicates better agreement with past data.  Black dots indicate sources with $\le0$ improvement score;
agreement decreases with addition of PAPER data (see Figures \ref{fig:SI_contour_bad} and \ref{fig:SI_contour_new}). 
This is most likely due to galactic, and Centaurus A, side lobes.    \label{fig:error_map}
}
\end{figure*}
